Time Series Bootstrapping For Solar Current

### 2021-12-07 deliverables/paper.Rmd
Cleaned up bootstrapping code, not quite operational

hour_plot_of_var(df, "GHI")
hour_plot_of_var(df, "current_out")
```

@@

#' Given a dataframe, return a matrix of bootstrap blocks
#'
#' @param df A dataframe of irradiance values
#' @return A matrix whose rows are bootstrap blocks
make_blocks_from_df <- function(df) {
  df <- df %>%
    mutate(date = lubridate::make_date(Year, Month, Day))
  # The number of blocks is the number of days
  number_of_blocks <- length(unique(df$date))
  # The length of a block is the number of
  # observations in each individual day.
  # In this case, we can simply look at the first one,
  # because all of the days have the same number of observations
  length_of_block <- nrow(df[df$date == unique(df$date)[1], ])
  blocks <- matrix(NA, nrow = number_of_blocks, ncol = length_of_block)
  print(dim(blocks))
  for (i in 1:number_of_blocks) {
    blocks[i, ] <- df$current_out[(i - 1) * length_of_block + 1 : (i * length_of_block)]
  }
  return(blocks)
}
# We have to use the modified DataFrame here,
# or else the assumptions about block size don't hold
make_blocks_from_df(df_high_irradiance)

>>>>

hour_plot_of_var(df, "GHI")
hour_plot_of_var(df, "current_out")
hour_plot_of_var(df, "declination_angle")
hour_plot_of_var(df, "solar_time")
hour_plot_of_var(df, "angle_sun_surface_degrees")
```

@@

#' Given a dataframe, return a matrix of bootstrap blocks
#'
#' @param df A dataframe of irradiance values
#' @return A matrix whose rows are bootstrap blocks
make_blocks_from_df <- function(df) {
  df <- df %>%
    mutate(date = lubridate::make_date(Year, Month, Day))
  # The number of blocks is the number of days
  number_of_blocks <- length(unique(df$date))
  # The length of a block is the number of
  # observations in each individual day.
  # In this case, we can simply look at the first one,
  # because all of the days have the same number of observations
  length_of_block <- nrow(df[df$date == unique(df$date)[1], ])
  blocks <- matrix(NA, nrow = number_of_blocks, ncol = length_of_block)
  start <- 1
  stop <- length_of_block
  for (i in 1:number_of_blocks) {
    # blocks[i, ] <- df$current_out[(i - 1) * length_of_block + 1 : (i * length_of_block)]
    blocks[i, ] <- df$current_out[start:stop]
    start <- start + length_of_block
    stop <- stop + length_of_block
  }
  return(blocks)
}
# We have to use the modified DataFrame here,
# or else the assumptions about block size don't hold
test <- make_blocks_from_df(df_high_irradiance)

block_bootstrap_estimates_from_df <- function(df, B=10000) {
  block_bootstrap_estimates <- rep(NA, B)
  blocks <- make_blocks_from_df(df)
  number_of_blocks <- nrow(blocks)
  for (i in 1:B) {
    # sample blocks
    idx <- sample(1:number_of_blocks, number_of_blocks, replace = TRUE)
    # Concatenate blocks at the given indices
    # This gives a "pseudo-dataset" containing resampled blocks
    block_bootstrap_estimates[i] <- mean(as.vector(t(blocks[idx, ])))
  }
  return(block_bootstrap_estimates)
}
test_est <- block_bootstrap_estimates_from_df(df_high_irradiance)
